\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{eurosym}

\usepackage{lastpage}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
%\renewcommand{\footrulewidth}{0pt}
\fancyfoot[C]{\bigskip\thepage/\pageref{LastPage}}


% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeGenItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingTWO}[1]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\newcommand{\resumeSubsubItem}[1]{\item\small{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{www.linkedin.com/in/kevin-keegan-engineer}{\Large Kevin Keegan} \quad {Dublin, Ireland}} & \href{mailto:kevinkeegans@gmail.com}{kevinkeegans@gmail.com}\\
  \href{www.linkedin.com/in/kevin-keegan-engineer}{www.linkedin.com/in/kevin-keegan-engineer} & +353-876428470 \\
\end{tabular*}


\section{Summary}
 Electronic Engineer with 3 years of industry experience.\\
1\textsuperscript{st} Class Honours Masters degree in Electronic \& Computer Engineering from University College Dublin.\\
Experienced in \textbf{Verilog, Python, C, Java, MATLAB \& Linux}.\\
Interested primarily in digital signal processing, digital ASIC design and embedded systems.
\bigskip
%---------SKILLS-----------
\section{Technical Skills}

  \resumeItemListStart
    \resumeSubItem{Languages/Tools} {Verilog, Python, Bash, Java, C/C++, LISP, ASM (MIPS32, 8051), MATLAB, Git, \LaTeX.}
    \resumeSubItem{Network Programming}{Experienced in TCP/IP Socket programming in Python, C \& Java.}
     \resumeSubItem{Concurrent Programming}{Experience in multiprocessing \& multi-threaded development.}
     \resumeSubItem{Operating Systems} {Professional experience developing in Linux and Windows environments.}
     \resumeSubItem{Embedded Systems} {Experience in front-end Digital Design (RTL) \& developing for microcontrollers such as Arduino, Micropython \& ADuC841. Knowledgeable in the use of Hardware Timers/Counters, Interrupt service routines and SPI communication.}
     \resumeSubItem{Digital Signal Processing} {Knowledgeable in Fourier analysis, digital filtering and digital communication theory.}
  \resumeItemListEnd
\bigskip

%-----------Experience-----------------

\section{Professional Experience}
\medskip
 \resumeSubHeadingListStart
    \resumeSubheading
      {Dialog Semiconductor, ASIC \& IP Division} {Dublin, Ireland}
      {Digital Design Engineer}{Jan 2020 -- Present}
      \resumeItemListStart
         \resumeGenItem{Front-End Digital Design} 
         \resumeGenItem{Developed software to automatically generate a Verilog implementation of a frequently redesigned block, along with its System Verilog testbench.}
      \resumeItemListEnd
      \bigskip
    \resumeSubheading
      {Susquehanna International Group (SIG)} {Dublin, Ireland}
      {Market Data Engineer}{Sept 2018 -- Nov 2019}
      \resumeItemListStart
      \resumeGenItem{Monitoring and maintaining critical market data systems.}
      \resumeGenItem{Pcap file analysis via Wireshark/tshark}
      \resumeGenItem{Developed validation tools to test new software before pushing to production.}
    \resumeGenItem{Implemented a system in Python \& Bash to archive daily market data recordings from company colocations to a central archive.}
     \resumeGenItem{
         Developed a set of scripts to analyse the latency of a  market data system when subject to a high data rates.}
         %mention fpga replaying
    \resumeGenItem{On call work. When on call, I was the first point of contact for issues regarding SIG's market data infrastructure.}
      \resumeItemListEnd
      \bigskip
     \resumeSubheading
      {Intel Corporation, Internet of Things and Wearables Group} {Kildare, Ireland}
      {Physical Design Engineer Intern}{Jan 2017 -- Aug 2017}
      \resumeItemListStart
         \resumeGenItem{Worked in a team designing a system in TCL to automate the design, layout \& routing of a custom CMOS block.}
      \resumeItemListEnd
      \bigskip
      \resumeSubheading
      {University College Dublin} {Dublin, Ireland}
      {Voluntary Teaching Assistant}{Sept 2015 -- Nov 2015}
      \resumeItemListStart
        \resumeGenItem{Voluntary Teaching Assistant in weekly laboratories for the engineering module,\\ 

EEEN20010	Computer Engineering I: Data Structures and Algorithms through C.}
      \resumeItemListEnd
\bigskip
      \resumeSubheading
      {FireEye, Inc.} {Dublin, Ireland}
      {Software Engineer Intern}{May 2015 - July 2015}
      \resumeItemListStart
        \resumeGenItem{Developed BASH scripts to facilitate and automate product testing.}
         \resumeGenItem{Built a customized, kickstarted centOS distro to include the configurations and packages necessary for running \& testing a company product.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\clearpage
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University College Dublin}{Dublin, Ireland}
      {Master of Engineering in Electronic \& Computer Engineering; 1st Class Honours}{Sept 2016 -- Sept 2018}
      \resumeItemListStart

      \resumeItem{GPA} {3.84/4.2}
        \resumeItem{\href{https://newsroom.intel.ie/news-releases/intel-partners-ucd-sponsor-masters-students/}{UCD Intel Masters Scholarship}}
          {Awarded by Intel to top five students entering ME program.}
      \resumeItemListEnd
    \resumeSubheading
      {University of California Los Angeles}{Los Angeles, CA}
      {Exchange - Electrical \& Electronic Engineering;  \textbf{GPA: 3.18/4.0}}{Jan 2016 -- Jun 2016}
    \resumeSubheading
      {University College Dublin}{Dublin, Ireland}
      {Bachelor of Science in Electrical \& Electronic Engineering; 1st Class Honours}{Sept 2013 -- Sept 2016}
      \resumeItemListStart
      \resumeItem{GPA} {4.09/4.2}
       \resumeItem{Entrance Scholar}
          {Awarded to top academic achievers entering UCD from secondary school.}
      \resumeItemListEnd
    \resumeSubheading
      {Col\'aiste Eoin}{Dublin, Ireland}
      {Irish Leaving Certificate;  \textbf{Points: 595}}{Sept 2007 -- Jun 2013}
  \resumeSubHeadingListEnd

%-----------Projects-----------------
\section{Projects}
  \resumeSubHeadingListStart 
  
    \resumeSubheading
      {UCD Masters Research Project}{Dublin, Ireland}
      {Digital and Analog Implementations of Visible Light Communication}{Sep 2017 -- May 2018}
      \resumeItemListStart
        \resumeGenItem{Project Thesis:  \textbf{\href{https://thekegman.github.io/Thesis.pdf} {thekegman.github.io/Thesis.pdf}}}
        \resumeGenItem{My project proposes a real-time digital, visible light communication system employing a form of On-Off Keying modulation. It is implemented using an Arduino UNO based LED-Photodiode communication link. It can successfully transfer files between computers over a distance of up to 1.8m.}
        \resumeGenItem{Software for this system was developed in C \& Python 3.}
      \resumeItemListEnd
    \resumeSubheading
     {Custom Guitar Tuner} {}
     {Analog amplifier \& DSP running on pyboard} {May 2020}
     \resumeItemListStart
     \resumeGenItem {Designed an Op-amp based electric guitar amplifier, implemented on a breadboard.}
     \resumeGenItem {This amplified signal is sampled using a pyboard microcontroller.}
     \resumeGenItem {The pyboard runs an auto-correlation based pitch estimation algorithm I developed.}
     \resumeGenItem {This algorithm estimates the fundamental frequency of the string being played.}
     \resumeGenItem {LEDs are used to indicate if the string is in-tune, flat or sharp.}
     \resumeItemListEnd      
\resumeSubheading
{Noodle Dance Camera Filter} {}
{Python Script} {Jan 2020}
\resumeItemListStart
\resumeGenItem {Python script using primarily numpy to recreate the popular Camera filter on TikTok.}
\resumeGenItem {Source: \textbf{\href{https://github.com/Thekegman/noodledance}{github.com/Thekegman/noodledance}}}
\resumeItemListEnd
\resumeSubheading
     {Spotify Collab Queue} {}
     {WebApp} {Feb 2019}
     \resumeItemListStart
     \resumeGenItem {Web app with a backend implemented in Python using the Flask framework.}
     \resumeGenItem {Using Spotify's API, this web app allows people to collaborate in what music is played by having them submit songs to a live queue.}
      \resumeGenItem {Source: \textbf{\href{https://github.com/Thekegman/spotify-collab-queue} {github.com/Thekegman/spotify-collab-queue}}}
     \resumeItemListEnd

%
\resumeSubheading
     {Nikon Trigger} {}
     {Microcontroller project} {Jan 2018}
     \resumeItemListStart
    
     \resumeGenItem {Program implemented for pyboard that uses an IR LED to remotely trigger a Nikon camera's shutter release.}
     \resumeGenItem {The 38kHz NEC protocol used by the Nikon `ML-L3" camera remote is replicated using PWM hardware available on pyboard.}
     \resumeGenItem {Source: \textbf{\href{https://github.com/Thekegman/Nikon-Trigger-for-MicroPython} {github.com/Thekegman/Nikon-Trigger-for-MicroPython}}}
     \resumeItemListEnd
%
\resumeSubheading
    {Android Apps} {}
     % {Guess That Word} {}
      {Implemented in Java, available on Google Play} {}
      \resumeItemListStart
        \resumeGenItem {Guess That Word} {May 2016} 
        \resumeGenItem {The Maze Extravaganza 3D - \textit{OpenGl}} {Aug 2013}
        \resumeGenItem {The Maze Extravaganza - \textit{36k+ downloads}} {July 2012}
        
        \resumeGenItem {
        Developer page: \textbf{\href{http://tiny.cc/x32oaz}{http://tiny.cc/x32oaz}}}
      \resumeItemListEnd

\resumeSubHeadingListEnd
     








%-----------ACTIVITIES & INTERESTS-----------------
%\section{Personal}
%  \resumeItemListStart
%    \resumeSubItem{Languages}{English, Spanish \& Irish.}
% 	\resumeSubItem{Guitar}{Grade 5 Classical Guitar, Trinity College London.}
% \resumeItemListEnd

%-------------------------------------------
\end{document}